\chapter{Introduction}
\label{ch:Introduction}

\vspace{-1cm}
\begin{center}
Eduard Hirsch
\end{center}


\section{Objectives and Motivation}

During the INTERLACE project, requirements for the transactional platform of an interest-free mutual credit system were collected and documented in deliverables D2.1\cite{INTERLACE_D21} and D3.1\cite{INTERLACE_D31}. The requirements were formulated precisely using ``Abstracts State Interaction Machines" (ASIMs). These ASIM specifications were used to create a working ICEF implementation,\footnote{\url{http://biomicsproject.eu/news/135-icef.html}\\ \url{https://github.com/InterlaceProject/icef}} which also has been described in D3.1.

The focus of the present report is on the creation of a working prototype that provides basic payment capabilities, thereby enabling a scalable implementation of a distributed ledger technology (DLT).

\section{Scope and Organization}
This report provides insights into the prototype created. It discusses the technologies used and provides feedback on how they have been applied in order to achieve a working implementation capable of accepting basic transfers.

Further, information is given on how the system can be installed and used for paying. The system can be therefore used to prove and test various use cases in order to understand the chosen DLT approach.

For production systems which might be built upon the INTERLACE prototype important features are discussed that need to be handled during the realisation of such a payment system. Thus the transition from a client-server to a p2p-based model together with possible challenges are described and exemple approaches explained.

Finally, an outlook is given which elaborates about possible scenarios that may be applied for a production scenario.

\newpage
